---
title: "TEST Workflow Template" 
author: "Author: Daniela Cassol (danielac@ucr.edu) and Thomas Girke (thomas.girke@ucr.edu)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`" 
output:
  BiocStyle::html_document:
    toc_float: true
    code_folding: show
package: systemPipeR
vignette: |
  %\VignetteIndexEntry{WF: TEST Workflow Template}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
fontsize: 14pt
bibliography: bibtex.bib
---

```{css, echo=FALSE}
pre code {
white-space: pre !important;
overflow-x: scroll !important;
word-break: keep-all !important;
word-wrap: initial !important;
}
```

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
options(width=60, max.print=1000)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")), 
    tidy.opts=list(width.cutoff=60), tidy=TRUE)
```

```{r setup_libraries, echo=FALSE, message=FALSE, warning=FALSE, spr='r'}
suppressPackageStartupMessages({
    library(systemPipeR)
})
```

# Introduction

This is a test template.

# Samples and environment settings

## Required packages and resources

The `systemPipeR` package needs to be loaded to perform the analysis steps shown in
this report [@H_Backman2016-bt].

```{r load_systempiper, eval=TRUE, message=FALSE, spr='r'}
library(systemPipeR)
```

## Experiment definition provided by `targets` file

The `targets` file defines all FASTQ files and sample
comparisons of the analysis workflow.

```{r load_targets, eval=TRUE, spr='r'}
targetspath <- system.file("extdata", "targetsPE.txt", package="systemPipeR")
targets <- read.delim(targetspath, comment.char = "#")[,1:4]
targets
```

# SYSargsList example

```{r wf_test, eval=TRUE, spr='sysargs'}
targetspath <- system.file("extdata/cwl/example/targets_example.txt", package="systemPipeR")
HW_mul <- SYSargsList(step_name = "Example",
                      targets=targetspath, 
                      wf_file="example.cwl", input_file="example.yml",
                      dir_path = system.file("extdata/cwl/example/", package="systemPipeR"), 
                      inputvars = c(Message = "_STRING_", SampleName = "_SAMPLE_"))
HW_mul
cmdlist(HW_mul)
```

# Version Information

```{r sessionInfo, spr='r'}
sessionInfo()
```

# Funding

This project was supported by funds from the National Institutes of Health (NIH).

# References
