---
title: "demo workflow" 
output:
  BiocStyle::html_document:
    toc_float: true
    code_folding: show
type: docs
---


## load_systempiper
```{r load_systempiper, eval=TRUE, message=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## load_targets
```{r load_targets, eval=TRUE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## construct_SYSargs2_trim_se
```{r construct_SYSargs2_trim_se, eval=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## preprocessing
```{r preprocessing, eval=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## fastq_report
```{r fastq_report, eval=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
``` 

## fastq_other
```{r fastq_other, eval=FALSE, spr='r', spr.dep='preprocessing'}
cat(rep("text", 5), sep = "\n")
``` 

## hisat_index
```{r hisat_index, eval=FALSE, spr='r', spr.dep='construct_SYSargs2_trim_se'}
cat(rep("text", 5), sep = "\n")
```

## hisat_SYSargs2_object
```{r hisat_SYSargs2_object, eval=TRUE, spr='sysargs'}
cat(rep("text", 5), sep = "\n")
```

## hisat_SYSargs2_singleM
```{r hisat_SYSargs2_singleM, eval=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## hisat2_clusterRun
```{r hisat2_clusterRun, eval=FALSE, spr='r', spr.dep='hisat_SYSargs2_object'}
cat(rep("text", 5), sep = "\n")
```

## check_files_exist
```{r check_files_exist, eval=FALSE, spr='r', spr.dep='hisat_SYSargs2_singleM'}
cat(rep("text", 5), sep = "\n")
```

## align_stats
```{r align_stats, eval=FALSE, spr='r', spr.dep='hisat_SYSargs2_singleM'}
cat(rep("text", 5), sep = "\n")
```

## align_stats_view
```{r align_stats_view, eval=TRUE, spr='sysargs'}
cat(rep("text", 5), sep = "\n")
```

## bam_urls
```{r bam_urls, eval=FALSE, spr='r', spr.dep='hisat_SYSargs2_singleM'}
cat(rep("text", 5), sep = "\n")
```

## read_counting1
```{r read_counting1, eval=FALSE, spr='r', spr.dep='hisat_SYSargs2_singleM'}
cat(rep("text", 5), sep = "\n")
```

## view_counts
```{r view_counts, eval=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## view_rpkm
```{r view_rpkm, eval=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## sample_tree
```{r sample_tree, eval=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## run_edger
```{r run_edger, eval=FALSE, spr='r', spr.dep='read_counting1'}
cat(rep("text", 5), sep = "\n")
```

## custom_annot
```{r custom_annot, eval=FALSE, spr='sysargs'}
cat(rep("text", 5), sep = "\n")
```

## filter_edger
```{r filter_edger, eval=FALSE, spr='r', spr.dep='run_edger'}
cat(rep("text", 5), sep = "\n")
```

## filter_degs
```{r filter_degs, eval=FALSE, spr='r', spr.dep='read_counting1; sample_tree'}
cat(rep("text", 5), sep = "\n")
```

## venn_diagram
```{r venn_diagram, eval=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## get_go_annot
```{r get_go_annot, eval=FALSE, spr='sysargs'}
cat(rep("text", 5), sep = "\n")
```

## go_enrich
```{r go_enrich, eval=FALSE, spr='r'}
cat(rep("text", 5), sep = "\n")
```

## go_plot
```{r go_plot, eval=FALSE, spr='sysargs'}
cat(rep("text", 5), sep = "\n")
```

## heatmap
```{r heatmap, eval=FALSE, spr='r', spr.dep='get_go_annot'}
cat(rep("text", 5), sep = "\n")
```


