---
title: "VAR-Seq Workflow Template" 
author: "Author: Daniela Cassol (danielac@ucr.edu) and Thomas Girke (thomas.girke@ucr.edu)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`" 
output:
  BiocStyle::pdf_document: default
  # BiocStyle::html_document:
  #   toc_float: true
  #   code_folding: show
package: systemPipeR
vignette: |
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{VAR-Seq Workflow Template}
  %\VignetteEngine{knitr::rmarkdown}
fontsize: 14pt
bibliography: bibtex.bib
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
options(width=60, max.print=1000)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")), 
    tidy.opts=list(width.cutoff=60), tidy=TRUE)
```

# VAR-Seq Workflow 

This workflow demonstrates how to use various utilities for building and running automated end-to-end analysis workflows for _`VAR-Seq`_ data. 

_**The full workflow can be found here: [HTML](http://www.bioconductor.org/packages/devel/data/experiment/vignettes/systemPipeRdata/inst/doc/systemPipeVARseq.html), [.Rmd](http://www.bioconductor.org/packages/devel/data/experiment/vignettes/systemPipeRdata/inst/doc/systemPipeVARseq.Rmd), and [.R](http://www.bioconductor.org/packages/devel/data/experiment/vignettes/systemPipeRdata/inst/doc/systemPipeVARseq.R).**_

## Loading package and workflow template

Load the _`VAR-Seq`_ sample workflow into your current working directory.

```{r genVar_workflow_single, eval=FALSE}
library(systemPipeRdata)
genWorkenvir(workflow="varseq")
setwd("varseq")
```

The working environment of the sample data loaded in the previous step contains
the following pre-configured directory structure. Directory names are indicated
in  <span style="color:grey">***bold***</span>. Users can change this
structure as needed, but need to adjust the code in their workflows
accordingly. 

* <span style="color:green">_**workflow/**_</span> (*e.g.* *varseq/*) 
    + This is the root directory of the R session running the workflow.
    + Run script ( *\*.Rmd*) and sample annotation (*targets.txt*) files are located here.
    + Note, this directory can have any name (*e.g.* <span style="color:green">_**varseq**_</span>, <span style="color:green">_**varseq**_</span>). Changing its name does not require any modifications in the run script(s).
  + **Important subdirectories**: 
    + <span style="color:green">_**param/**_</span> 
        + Stores non-CWL parameter files such as: *\*.param*, *\*.tmpl* and *\*.run.sh*. These files are only required for backwards compatibility to run old workflows using the previous custom command-line interface.
        + <span style="color:green">_**param/cwl/**_</span>: This subdirectory stores all the CWL parameter files. To organize workflows, each can have its own subdirectory, where all `CWL param` and `input.yml` files need to be in the same subdirectory. 
    + <span style="color:green">_**data/**_ </span>
        + FASTQ files
        + FASTA file of reference (*e.g.* reference genome)
        + Annotation files
        + etc.
    + <span style="color:green">_**results/**_</span>
        + Analysis results are usually written to this directory, including: alignment, variant and peak files (BAM, VCF, BED); tabular result files; and image/plot files
        + Note, the user has the option to organize results files for a given sample and analysis step in a separate subdirectory.

The following parameter files are included in each workflow template:

1. *`targets.txt`*: initial one provided by user; downstream *`targets_*.txt`* files are generated automatically
2. *`*.param/cwl`*: defines parameter for input/output file operations, *e.g.*:
    + *`hisat2-se/hisat2-mapping-se.cwl`* 
    + *`hisat2-se/hisat2-mapping-se.yml`*
3. *`*_run.sh`*: optional bash scripts 
4. Configuration files for computer cluster environments (skip on single machines):
    + *`.batchtools.conf.R`*: defines the type of scheduler for *`batchtools`* pointing to template file of cluster, and located in user's home directory
    + *`*.tmpl`*: specifies parameters of scheduler used by a system, *e.g.* Torque, SGE, Slurm, etc.

## Run workflow

Next, run the chosen sample workflow _`systemPipeVARseq`_ ([.Rmd](http://www.bioconductor.org/packages/devel/data/experiment/vignettes/systemPipeRdata/inst/doc/systemPipeVARseq.Rmd)) by executing from the command-line _`make -B`_ within the _`varseq`_ directory. Alternatively, one can run the code from the provided _`*.Rmd`_ template file from within R interactively. 

Workflow includes following steps:

1. Read preprocessing
    + Quality filtering (trimming)
    + FASTQ quality report
2. Alignments: _`gsnap`_, _`bwa`_
3. Variant calling: _`VariantTools`_, _`GATK`_, _`BCFtools`_
4. Variant filtering: _`VariantTools`_ and _`VariantAnnotation`_
5. Variant annotation: _`VariantAnnotation`_
6. Combine results from many samples
7. Summary statistics of samples

# Version Information

```{r sessionInfo}
sessionInfo()
```

# Funding

This project is funded by NSF award ABI-1661152.